\documentclass[line,margin]{res} 
\usepackage{hyperref}

\textheight=700pt

\addtolength{\topmargin}{-.4in}

\begin{document}


\name{\Huge{Kathryn M Roy}}

\noindent
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{https://github.com/MaeveMonster}{github.com/MaeveMonster\\}}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{(585) 755-7242}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}}


%\begin{flushright}
%\href{https://github.com/MaeveMonster}{github.com/MaeveMonster}\\
%(585) 755-7242\\
%\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}
%\end{flushright}

\begin{resume}

%-------------------------------------------------------------------------------
%   OBJECTIVE
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
A co-op or internship for the summer of 2018.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
%\section{CONTACT}
%1644 Shallow Creek Trail, Webster NY, 14580 \hfill %\href{https://github.com/MaeveMonster}{github.com/MaeveMonster}\\(585) 755-7242 \hfill %\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Rochester Institute of Technology}, Rochester, NY\hfill
    \textbf{2016-2020}\\
{\sl Bachelor of Science}, Video Game Design and Development, May 2020\hfill GPA: 3.51
\\
{\sl Dean's List} - Golisano College of Computing and Information Sciences\hfill \\ Fall 2016, Spring 2017
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}
\textbf{Languages}: C\#, C++, Python, Java\\
\textbf{Game Development Software}: Unity 5.x\\
\textbf{3D Modeling Software}: Autodesk Maya 2017
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
    \href{https://github.com/MaeveMonster/GumioGame}{\textbf{Gumio Game}}
    {\sl (C\# Monogame)}\hfill \textbf{2017}\\ 
    A 2D platformer about a chewed piece of gum that jumps on and over platforms to 
	reach the end of the level. In this group project, my role as team-lead involved delegation of tasks, keeping track of team goals and milestones, and collaboration in planning, writing, and debugging code and documentation.
\par
    \href{https://github.com/MaeveMonster/PalindromicSummation}
    {\textbf{Palindromic Summation}}{\sl (Java)}\hfill \textbf{2015}\\
    A Java console application that finds a series of numbers whose base 10 and binary representations are palindromic. Solo project.
\par
    \href{https://github.com/MaeveMonster/BaseConverter}{\textbf{Base Converter}}
    {\sl (Java)}\hfill \textbf{2015}\\ 
    A solo project in which I created a Java console application that converts numbers between bases.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{WORK EXPERIENCE}
\employer{\textbf{Fall 2016-Present}}
\location{Rochester, NY}
\dates{{\sl Student Employee}}
\title{\textbf{Ctrl Alt DELi}}
\begin{position}
    Cashiering, make-to-order food preparation, grab-and-go food preparation
\end{position}
\employer{\textbf{Fall 2015-Present}}
\location{Webster, NY}
\dates{{\sl Associate Trainer}}
\title{\textbf{Panera Bread}}
\begin{position}
    Training new associates in cashiering, food preparation, barista, and table-bussing
\end{position}
\employer{\textbf{Fall 2013-Spring 2015}}
\location{Webster, NY}
\dates{{\sl Page}}
\title{\textbf{Webster Public Library}}
\begin{position}
    Replaced items within the library, cleaned, and kept shelves organized.
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
\section{ACTIVITIES}
\href{https://csh.rit.edu}{\textbf{Computer Science House}}
{\sl (organization)}\hfill
\textbf{Current Member}\\
A special interest house at RIT which encourages group collaboration on technical 
projects and provides access and funds to develop those projects.
resources, and more\\
\textbf{Events}: 
Technical seminars, hackathons, coding competitions, tutoring\\\\
\textbf{Other Interests/Activities}\\
Muay Thai Kickboxing, RIT Pep Band: Flutist, Girl Scouts: Gold Award Recipient, Alpine Skiing, Longboarding, Camping
%-------------------------------------------------------------------------------

\end{resume}

%subscript
%\scriptsize{References on request} \hfill 

\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\scriptsize{References on request}}

\end{document}