\documentclass[line,margin]{res} 
\usepackage{hyperref}

\textheight=700pt

\addtolength{\topmargin}{-.4in}

\begin{document}


\name{\Huge{Kathryn M Roy}}

\noindent
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{https://github.com/MaeveMonster}{github.com/MaeveMonster\\}}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{(585) 755-7242}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}}


%\begin{flushright}
%\href{https://github.com/MaeveMonster}{github.com/MaeveMonster}\\
%(585) 755-7242\\
%\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}
%\end{flushright}

\begin{resume}

%-------------------------------------------------------------------------------
%   OBJECTIVE
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
A part-time job in software engineering for the spring of 2019.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
%\section{CONTACT}
%1644 Shallow Creek Trail, Webster NY, 14580 \hfill %\href{https://github.com/MaeveMonster}{github.com/MaeveMonster}\\(585) 755-7242 \hfill %\href{mailto:kmr8172@g.rit.edu}{kmr8172@g.rit.edu}

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Rochester Institute of Technology}, Rochester, NY\hfill
    \textbf{2016-2020}\\
{\sl Bachelor of Science}, Video Game Design and Development, May 2020
\\
{\sl Dean's List} - Golisano College of Computing and Information Sciences,\hfill \\ Fall 2016 and Spring 2017
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}
\textbf{Languages}: C\#, C++, Java, Kotlin\\
\textbf{Game Development Software}: Unity 5.x\\
\textbf{3D Modeling Software}: Autodesk Maya 2017
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
    \href{https://github.com/MaeveMonster/GumioGame}{\textbf{Gumio Game}}
    {\sl http://bit.ly/GumioGame}\hfill \textbf{2017}\\ 
    A 2D platformer made in C\# Monogame about a chewed piece of gum that jumps on and over platforms to 
	reach the end of the level. In this group project, my role as team-lead involved delegation of tasks, keeping track of team goals and milestones, and collaboration in planning, writing, and debugging code and documentation.
	
	\par
    \href{https://github.com/MaeveMonster/DesertPandemonium}{\textbf{Desert Pandemonium}}
    {\sl http://bit.ly/DesertPandemonium}\hfill \textbf{2017}\\ 
    A Unity experiment to procedurally generate game components in both uniform and non-uniform distributions.

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{WORK EXPERIENCE}
\employer{\textbf{Jan 2019-Present}}
\location{Rochester, NY}
\dates{{\sl Software Engineer Intern}}
\title{\textbf{Bryx}}
\begin{position}
    Worked on software for alerting first-responders of incoming calls in Kotlin, iOS, and Android. Worked on geocoding and audio design for mobile alert-tones and station alert-tones. In react, built a website user-interface for an API that allowed for testing of various geocoding software.
\end{position}
\employer{\textbf{May 2018-December 2018}}
\location{Liverpool, NY}
\dates{{\sl Part-time Software Engineer}}
\title{\textbf{Lockheed Martin Corporation}}
\begin{position}
    Worked on a scrum team to write, test, and integrate code for many projects including a simulation program for the E2D Advanced Hawkeye radar system.
\end{position}
\employer{\textbf{Fall 2016-Present}}
\location{Rochester, NY}
\dates{{\sl Student Employee}}
\title{\textbf{Ctrl Alt DELi}}
\begin{position}
    Worked as a cashier, prepared make-to-order food, prepared grab-and-go food
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
\section{ACTIVITIES}
\href{https://csh.rit.edu}{\textbf{Computer Science House}}
\hfill
\textbf{Friend of Floor}\\
A special interest house at RIT which encourages group collaboration on technical 
projects and provides access and funds to develop those projects, resources, and more\\
\textbf{Events}: 
Technical seminars, hackathons, coding competitions, tutoring\\
\\\textbf{Other Interests/Activities}\\
Muay Thai Kickboxing, RIT Pep Band: Flutist, Alpine Skiing, Longboarding, Camping

\textbf{Girl Scouts} \hfill \textbf{Ambassador Level Gold Award Recipient}\\
Created a community vegetable garden to benefit a local food cupboard.
%-------------------------------------------------------------------------------

\end{resume}
\end{document}